---
title: "My dashboard"
format: 
  dashboard:
    theme: 
      - sandstone
      - style/custom-light.scss
---

<!-- Themes: https://bootswatch.com/ -->
<!-- https://quarto.org/docs/dashboards/theming.html  -->


# {.sidebar}
This is my page global sidebar

```{r}
library(tidyverse)
library(plotly)
library(reactable)


# https://rpubs.com/zac-garland/highcharter-chartbook 
```


# Page 1
## Row 1 {height="30%"}
### Column 1

```{r}
#| title: Speed vs. distance

p <- ggplot(cars, aes(speed, dist)) + geom_point()
ggplotly(p)
```

### Column 2
```{r}
# Título dinâmico
n_cars <- nrow(mpg)
cat("title=", "Drive types of", n_cars, "cars" )

ggplot(mpg, aes(x = drv)) + geom_bar()
```

## Row 2 {height="70%"}
### Card orientation: column 
```{r}
#| title: One cell = one card
#| layout-ncol: 2
ggplot(mpg, aes(x = cty, y=hwy)) + geom_point()

ggplot(mpg, aes(x = drv)) + geom_bar()

```

::: {.card title="One cell = one card"}
```{r}
plot(women)
plot(cars)
```
:::

# Local sidebar
## Colunm 1 {.sidebar}
This is my page level sidebar

## Colunm 2
### Row 1
```{r}
plot(women)
```

```{r}
plot(women)
```


### Row 2
```{r}
plot(women)
```



# Value Boxes
## Value Boxes  {height=30%}
```{r}
#| label: calculate-values

lowest_mileage_cty <- mpg |>
  filter(cty == min(cty)) |>
  distinct(cty) |>
  pull(cty)


highest_mileage_cty <- mpg |>
  filter(cty == max(cty)) |>
  distinct(cty) |>
  pull(cty)


rounded_mean_city_mileage <- mpg |>
  summarize(round(mean(cty), 2)) |>
  pull()
```

```{r}
#| content: valuebox
#| title: "Least efficient"
#| icon: fuel-pump-fill
#| color: danger

list(value = paste(lowest_mileage_cty), "mpg")
```


```{r}
#| content: valuebox
#| title: "Most efficient"

list(
  icon = "fuel-pump",
  color = "success",
  value = paste(highest_mileage_cty), "mpg")
```


::: {.valuebox icon="fuel-pump" color="secondary"}
Average city mileage

`{r} rounded_mean_city_mileage` mpg
:::


## Row 1 {height=70%}
### Column 1
```{r}
p1 <- ggplot(cars, aes(speed, dist)) + geom_point()
ggplotly(p1)
```

### Column 2 
```{r}
p2 <-  ggplot(women, aes(weight, height)) + geom_point()
ggplotly(p2)
```








# Testando Layout 2
## Row 1 {height=60%}
### Column 1
```{r}
p1 <- ggplot(cars, aes(speed, dist)) + geom_point()
ggplotly(p1)
```

### Column 2
```{r}
p2 <-  ggplot(women, aes(weight, height)) + geom_point()
ggplotly(p2)
```

```{r}
plot(cars)
```


## Row 2 {height=40%} {.tabset}
```{r}
plot(women)
```

```{r}
plot(cars)

```





# Tabs
## Row 1 {height=60%}
### Column 1
```{r}
p1 <- ggplot(cars, aes(speed, dist)) + geom_point()
ggplotly(p1)
```

### Column 2  {.tabset}
```{r}
p2 <-  ggplot(women, aes(weight, height)) + geom_point()
ggplotly(p2)
```

```{r}
plot(cars)
```


## Row 2 {height=40%} 
### Column 1
hello

### Column 2  {.tabset}
```{r}
plot(women)
```

```{r}
plot(cars)

```


